Advanced Machine Learning\\Final Report

### 2018-12-27 minutia/AML-report/main.tex
writeup: clean commencement

\date{\today}

@@

According to the attributes that are observed from the given problem, the final implemented method has been selected. The significant characteristics of the given problem are as follows:
\begin{itemize}
    \item Model is not provided.
    \item Dataset is only a set of generated samples.
    \item Inaccessible agent therefore online learning is not possible.
    \item Evidently high correlation between consequent year samples.
\end{itemize}

@@

>>>>

\date{December 19, 2018}

@@

According to the attributes that are observed from the given problem, the final implemented method has been selected. The significant characteristics of the given problem are as follows:
\begin{itemize}
    \item Model is not provided.
    \item Dataset is only a set of generated samples.
    \item Episodic problem.
    \item Inaccessible agent therefore online learning is not possible.
    \item Evidently high correlation between consequent year samples.
\end{itemize}

@@

\section{Results}
Results are provided as dataset which in a policy column is appended. policy says which action should be taken at the end of each year for each episodes. From the loss values observed while training the network and the performance during the run-time, the results seems to be promising. I have also performed a set of measurements on after training like accuracy which shows the method works in operational regions.
